TITLE

### 2021-02-26 outputs/Paper.Rmd
update

```{r restaurant1, fig.cap = "Restaurant numbers and types", echo=FALSE,fig.width=8, fig.height=5}
R1<-simulated_data%>%
  ggplot(aes(x = simulated_data$Q2,fill = type)) +
  geom_bar(stat = "count", position = "dodge") +
  labs(title = "More restuarants are loacted in City of Toronto and Peel Region",x="Regions") +
  theme_minimal() +
  scale_fill_manual(values = c("Red", "Blue"))

R2<-simulated_data%>%
  ggplot(aes(x = simulated_data$Q3 ,fill = type)) +
  geom_bar(stat = "count", position = "dodge") +
  labs(title = "More restuarants in GTA are casual dinning ",x="Regions") +
  theme_minimal() +
  scale_fill_manual(values = c("Red", "Blue"))

@@

* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor. From the pie charts (Figure \@ref(fig:franchise)), we found the portion of franchise rate in treated group is slightly lower than control group. We assume in treated group, the branch franchise restaurants should follow the rules by the head office. Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.

```{r franchise, fig.cap = "Restaurant franchise distribution",echo=FALSE, fig.width=10, fig.height=4}

Pie1<-control_data%>%
  ggplot(aes(x = control_data$Q4 ,fill = Q4)) +
  geom_bar(stat = "count", position = "dodge") +
  coord_polar("y", start=0)+   #Create a pie chart based on the barplot
  labs(title = "Franchise restaurants slightly decrease in treated group ",x="Regions",y="Count in control group") +
  theme_minimal() +
  scale_fill_manual(values = c("Red", "Blue"))

Pie2<-treated_data%>%
  ggplot(aes(x = treated_data$Q4 ,fill = Q4)) +
  geom_bar(stat = "count", position = "dodge") +
  coord_polar("y", start=0)+
  labs(title = "",x="Regions", y="Count in treated group") +
  theme_minimal() +
  scale_fill_manual(values = c("Red", "Blue"))

@@

```{r employee, fig.cap = "Empoyee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
cxc <- 
  simulated_data%>%
  ggplot(aes(x = simulated_data$Q8 ,fill = type)) +
  geom_bar(width = 0.7,position = "dodge") + 
  coord_polar()+
  scale_fill_manual(values = c("Red", "Blue"))+
  labs(title = "Almost 0 restaurant has more than 30 employees in control group",x="", y="Count") +
  theme_minimal()

@@

library(ggthemes)
# Treated group
rd1<-
  ggplot(simulated_data, aes(x = simulated_data$Q13/1000, fill=type)) +
  geom_histogram(position = "dodge", bins = 30,binwidth = 5) +
  scale_fill_manual(values = c("red", "blue"))+
  labs(title="Revenue Distributions Move to the right", x="Renvenue (Thousands)", y="Count")+
  geom_density()+
  theme_calc()

@@

# Fixed costs 
fixc1<-
  ggplot(simulated_data, aes(fill= type, x=Q11)) +
  geom_bar(stat="count", width = 0.6,position = "dodge")+
  scale_fill_manual(values = c("red", "blue"))+
    ggtitle("Fixed costs increased in treated group and remain same in control group") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()
fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# flex cost
flexc1<-
    ggplot(simulated_data, aes(fill= type, x=Q12)) +
    geom_bar(stat="count", width = 0.7, position = "dodge")+
    scale_fill_manual(values = c("red", "blue"))+
    ggtitle("Flexible costs increased in most of treated group restaurants") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()
flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

>>>>

```{r restaurant1, fig.cap = "Restaurant numbers and types", echo=FALSE,fig.width=8, fig.height=5}
R1<-simulated_data%>%
  ggplot(aes(x = simulated_data$Q2,fill = type)) +
  geom_bar(stat = "count", position = "dodge") +
  labs(title = "More restuarants are loacted in City of Toronto and Peel Region",x="Regions") +
  theme_minimal() +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))

R2<-simulated_data%>%
  ggplot(aes(x = simulated_data$Q3 ,fill = type)) +
  geom_bar(stat = "count", position = "dodge") +
  labs(title = "More restuarants in GTA are casual dinning ",x="Regions") +
  theme_minimal() +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))

@@

* The attributes of the restaurant determine its management mode, so whether the restaurant is a franchise is quite important factor. From the pie charts, we found the portion of franchise rate in treated group is slightly lower than control group. We assume in treated group, the branch franchise restaurants should follow the rules by the head office. Considering the potential cost of COVID issues, chain restaurants will face greater risks, which is why they are less likely to be in the treated group.

(Figure \@ref(fig:pie1))

```{r pie1, fig.cap = "Restaurant franchise distribution",echo=FALSE, fig.width=10, fig.height=4}

Pie1<-control_data%>%
  ggplot(aes(x = control_data$Q4 ,fill = Q4)) +
  geom_bar(stat = "count", position = "dodge") +
  coord_polar("y", start=0)+   #Create a pie chart based on the barplot
  labs(title = "Franchise restaurants slightly decrease in treated group ",x="Regions",y="Count in control group") +
  theme_minimal() +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))

Pie2<-treated_data%>%
  ggplot(aes(x = treated_data$Q4 ,fill = Q4)) +
  geom_bar(stat = "count", position = "dodge") +
  coord_polar("y", start=0)+
  labs(title = "",x="Regions", y="Count in treated group") +
  theme_minimal() +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))

@@

```{r employee, fig.cap = "Empoyee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}
cxc <- 
  simulated_data%>%
  ggplot(aes(x = simulated_data$Q8 ,fill = type)) +
  geom_bar(width = 0.7,position = "dodge") + 
  coord_polar()+
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
  labs(title = "Almost 0 restaurant has more than 30 employees in control group",x="", y="Count") +
  theme_minimal()

@@

library(ggthemes)
# Treated group
rd1<-
  ggplot(simulated_data, aes(x = simulated_data$Q13/1000, fill=type)) +
  geom_histogram(position = "dodge", bins = 30,binwidth = 5) +
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
  labs(title="Revenue Distributions Move to the right", x="Renvenue (Thousands)", y="Count")+
  geom_density()+
  theme_calc()

@@

# Fixed costs 
fixc1<-
  ggplot(simulated_data, aes(fill= type, x=Q11)) +
  geom_bar(stat="count", width = 0.6,position = "dodge")+
  scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
    ggtitle("Fixed costs increased in treated group and remain same in control group") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()
fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title

# flex cost
flexc1<-
    ggplot(simulated_data, aes(fill= type, x=Q12)) +
    geom_bar(stat="count", width = 0.7, position = "dodge")+
    scale_fill_manual(values = c("#E85C34", "#2C92D5"))+
    ggtitle("Flexible costs increased in most of treated group restaurants") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()
flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title
